\documentclass[10pt,letterpaper,sans]{moderncv}

% Style
\moderncvstyle{classic}
\moderncvcolor{blue}

% Encoding & layout
\usepackage[utf8]{inputenc}
\usepackage[scale=0.92, top=1.2cm, bottom=1.2cm, left=1.3cm, right=1.3cm]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}
\usepackage{fontawesome5}

% Reduce vertical spacing
\AtBeginDocument{\recomputelengths}
\setlength{\makecvtitlenamewidth}{10cm}

% Personal information
\name{Alejandro}{Millan}
\email{amilland29@gmail.com}
\phone[mobile]{+1 (612) 328-9594}
\homepage{amillan.info}
\social[linkedin]{amilland}
\social[github]{alejandromillan29}
\extrainfo{US Citizen — Authorized to work in the United States}
\pagenumbering{gobble}

\begin{document}

\makecvtitle
\vspace{-1.2em}

%----- Profile -----
\section{Profile}
Senior Frontend Engineer with 6+ years of experience building scalable web and mobile applications in fintech, banking, e-commerce, and event platforms. Strong background in frontend architecture, performance optimization, and hands-on development using Vue.js, Angular, and TypeScript. Proven ability to lead complex initiatives end‑to‑end while remaining a highly productive individual contributor. Experienced working with cloud-based architectures, CI/CD pipelines, and cross-functional teams in Agile environments.

\vspace{-0.4em}

%----- Technical Skills -----
\section{Technical Skills}
\cvitem{Frontend Engineering}{JavaScript (ES6+), TypeScript, Vue.js (Vue 3), Angular, Nuxt, Ionic, HTML5, CSS3, Tailwind, Bootstrap, Client-Side Rendering (CSR), Server-Side Rendering (SSR), PWAs, Frontend architecture, performance optimization, scalable UI systems}
\cvitem{Cloud \& Backend Integration}{Firebase (Functions, Firestore, Authentication, Messaging, App Check, Analytics), AWS (Lambda, API Gateway, Amplify, Elastic Beanstalk), RESTful APIs, Axios, Firebase SDK}
\cvitem{Testing, Tooling \& DevOps}{Cypress, Appium, Vitest, Jasmine, Karma, Vite, Webpack, ESLint, Prettier, npm, CI/CD with GitHub Actions and Fastlane}
\cvitem{Collaboration \& Delivery}{Agile / Scrum methodologies, Git-based workflows, Jira, GitHub, Bitbucket, Slack, Microsoft Teams}
\cvitem{Languages}{English (Fluent), Spanish (Native)}

\vspace{-0.4em}

%----- Professional Experience -----
\section{Professional Experience}

\cventry{2023 -- Present}{Frontend Tech Lead / Senior Frontend Engineer}{Blue Core S.A.}{}{}{
\begin{itemize}
  \item Led frontend architecture and hands-on development of a large-scale digital banking platform serving 200,000+ users.
  \item Designed and implemented 8+ critical customer journeys including onboarding, account recovery, and user reactivation.
  \item Built production-ready interfaces using Angular 19 and TypeScript, consuming RESTful APIs backed by AWS Lambda and API Gateway.
  \item Integrated third-party services for biometric identity validation and online appointment scheduling (FacePhi, Microsoft Bookings).
  \item Established frontend standards and best practices that improved code maintainability, performance, and scalability.
  \item Performed code reviews, mentored engineers, and collaborated closely with backend, QA, and product teams while remaining an active individual contributor.
\end{itemize}}

\vspace{-0.2em}

\vspace{-0.2em}

\cventry{2021 -- 2022}{Frontend Engineer (Quality & Automation)}{Blue Core S.A.}{}{}{
\begin{itemize}
  \item Improved frontend reliability by implementing end-to-end (E2E) automation across web and mobile platforms using Cypress and Appium.
  \item Built and maintained CI/CD pipelines with GitHub Actions and Fastlane to automate testing, builds, and releases for iOS and Android.
  \item Collaborated with frontend and backend teams to identify performance bottlenecks and prevent regressions in critical user flows.
\end{itemize}}

\vspace{-0.2em}

\cventry{2020}{Frontend Developer}{Bath \& Body Works}{}{}{
\begin{itemize}
  \item Maintained and enhanced 8 e-commerce storefronts across multiple Latin American markets.
  \item Implemented UI updates, promotional features, and CMS-driven content using VTEX.
  \item Collaborated with design and business teams to ensure consistent branding and improved conversion rates.
\end{itemize}}

\vspace{-0.2em}

\cventry{2019}{Junior Web Developer}{Venmetro Inc.}{}{}{
\begin{itemize}
  \item Contributed to the development of a fintech web platform serving ~1,800 monthly users.
  \item Built and maintained frontend components using Vue.js while working alongside a Ruby on Rails backend.
  \item Strengthened full-stack fundamentals and participated in feature delivery and bug-fix cycles.
\end{itemize}}

\vspace{-0.4em}

%----- Entrepreneurial Experience -----
\section{Entrepreneurial Experience}

\cventry{2022 -- Present}{Lead Developer / Founder}{One Spot Inc.}{}{}{
\begin{itemize}
  \item Architected and led development of a web and mobile ticketing platform with 8,000+ registered users and 15,000+ tickets sold.
  \item Designed the full frontend architecture using Vue.js, Ionic, and Capacitor, supporting real-time updates and responsive mobile experiences.
  \item Implemented authentication, push notifications, analytics, and secure API consumption using Firebase services.
  \item Integrated credit card payment gateways (NMI) and local digital wallets, enabling secure, high-volume transactions.
  \item Managed end-to-end delivery, including cloud infrastructure, CI/CD, and production releases to the App Store and Google Play.
\end{itemize}}

%----- Education -----
\section{Education}
\cventry{}{Master's Degree in Software Engineering}{}{Panama}{}{}
\cventry{}{Bachelor's Degree in Systems Engineering}{}{Panama}{}{}

\end{document}
