\documentclass[10pt,letterpaper,sans]{moderncv}

% Style
\moderncvstyle{classic}
\moderncvcolor{blue}

% Encoding & layout
\usepackage[utf8]{inputenc}
\usepackage[scale=0.92, top=1.2cm, bottom=1.2cm, left=1.3cm, right=1.3cm]{geometry}
\setlength{\hintscolumnwidth}{3.2cm} % Slightly wider for "Solution Architecture" label
\usepackage{fontawesome5}
\usepackage{needspace}

% Reduce vertical spacing
\AtBeginDocument{\recomputelengths}
\setlength{\makecvtitlenamewidth}{10cm}

% Personal information
\name{Alejandro}{Millan}
\email{amilland29@gmail.com}
\phone[mobile]{+1 (612) 328-9594}
\homepage{amillan.info}
\social[linkedin]{amilland}
\social[github]{alejandromillan29}
% STRATEGY: Bold and explicit about status and relocation to bypass geo-filters
\extrainfo{\textbf{US Citizen} $\bullet$ \textbf{Authorized to work in the United States}}
\pagenumbering{gobble}

% ---- Tighten spacing globally (ATS-safe) ----
\usepackage{enumitem}
\setlist[itemize]{topsep=2pt, itemsep=2pt, parsep=0pt, partopsep=0pt}

\setlength{\parskip}{2pt}
\setlength{\parsep}{0pt}

\begin{document}

\makecvtitle
\vspace{-2.0em}

%----- Profile -----
% STRATEGY: Shifted from "Developer" to "Bridge between Business and Tech"
\section{Profile}
Solutions Engineer and Technical Lead with 6+ years of experience architecting customer-facing platforms. Proven track record of bridging the gap between complex business requirements and scalable technical execution. Deep expertise in cloud architectures (AWS/Firebase) and API integrations, combined with a founder's mindset for understanding client needs, driving technical discovery, and delivering value-driven Proofs of Concept (PoCs).

\vspace{-0.4em}

%----- Technical Skills -----
\section{Skills \& Solution Architecture}
% STRATEGY: Added "Client-Facing" skills first to signal SE readiness
\cvitem{Solution Design \& Client-Facing}{Technical Discovery, Requirements Analysis, Stakeholder Management, API Integration Strategy, Proof of Concept (PoC) Development, Technical Demos, Agile/Scrum Leadership}
\cvitem{Cloud \& Backend}{AWS (Lambda, API Gateway, Amplify, Elastic Beanstalk), Node.js, Firebase (Functions, Firestore, Auth, Analytics), RESTful API Design, SQL \& NoSQL Database Modeling}
\cvitem{Frontend Systems}{JavaScript (ES6+), TypeScript, Vue.js, Angular, React, Ionic, Scalable Architecture, PWA Development, Performance Optimization}
\cvitem{DevOps \& Tooling}{CI/CD Pipelines (GitHub Actions, Fastlane), Cypress, Appium, Docker basics, Git-based workflows}
\cvitem{Languages}{English (Fluent), Spanish (Native)}

\vspace{-0.4em}

%----- Professional Experience -----
\section{Professional Experience}

% STRATEGY: Changed title to emphasize Leadership/Solutions over just "Frontend"
\cventry{2023 -- Present}{Solutions Lead / Senior Engineer}{Blue Core S.A.}{}{}{
\begin{itemize}
  \item Architected 8+ critical customer journeys (onboarding, account recovery) to resolve user drop-off issues, serving a user base of 200,000+.
  \item Served as the technical liaison between product managers, backend engineers, and business stakeholders to translate functional requirements into technical specifications.
  \item Led integration of biometric (FacePhi) and scheduling (MS Bookings) services with secure data workflows.
  \item Built scalable interfaces using AWS Lambda and API Gateway for high-concurrency environments.
  \item Established integration best practices to improve delivery speed and system reliability.
\end{itemize}}

\vspace{-0.2em}

% STRATEGY: This is your "Star Player" section for SE roles. Emphasizing the "Founder" aspect = "Business Awareness"
\cventry{2022 -- Present}{Founder / Lead Solutions Engineer}{One Spot Inc.}{}{}{
\begin{itemize}
  \item Acted as the primary technical point of contact for enterprise clients, leading discovery sessions to gather requirements and propose custom integration solutions.
  \item Designed and delivered a full-stack ticketing platform supporting 8,000+ users, managing the entire lifecycle from pre-sales technical consulting to final implementation.
  \item Orchestrated complex payment gateway integrations (NMI) and digital wallet workflows, ensuring PCI compliance and secure transaction processing.
  \item Implemented a serverless architecture using Firebase to handle real-time data syncing, authentication, and push notifications for high-traffic events.
  \item Led technical account management and onboarding to ensure seamless client adoption.
\end{itemize}}

\vspace{-0.2em}

\cventry{2021 -- 2022}{Frontend Engineer (Quality \& Automation)}{Blue Core S.A.}{}{}{
\begin{itemize}
  \item Boosted reliability by building Cypress and Appium automated test suites for web and mobile.
  \item Streamlined iOS/Android deployments using GitHub Actions and Fastlane to reduce time-to-market.
\end{itemize}}

\vspace{-0.2em}

\cventry{2020}{Frontend Developer}{Bath \& Body Works}{}{}{
\begin{itemize}
  \item Managed technical operations for 8 Latin American e-commerce storefronts, ensuring uptime and brand consistency.
  \item Implemented VTEX CMS strategies, enabling marketing teams to launch promotional features rapidly.
  \item Partnered with design teams to execute UI/UX improvements that directly impacted conversion rates.
\end{itemize}}

\vspace{-0.2em}

\cventry{2019}{Junior Web Developer}{Venmetro Inc.}{}{}{
\begin{itemize}
  \item Built reusable Vue.js components and integrated Ruby on Rails APIs for a fintech platform.
  \item Delivered features and bug fixes in Agile sprints for 1,800+ monthly active users.
\end{itemize}}

\vspace{-0.2em}

%----- Education -----
\section{Education}
\cventry{}{Master's Degree in Software Engineering}{}{}{}{}
\cventry{}{Bachelor's Degree in Systems Engineering}{}{}{}{}

\end{document}